Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 background.tex
replace a reference in Section2.3

For a parallel application requiring multiple compute nodes, the job placement policy refers to the way of assigning the required number of nodes to the application by system software such as the batch scheduler~\cite{xu-cluster14}. In this work, we study two alternative placement policies considered by the community for dragonfly systems:

>>>>

For a parallel application requiring multiple compute nodes, the job placement policy refers to the way of assigning the required number of nodes to the application by system software such as the batch scheduler~\cite{tsafrir-tpds-2007}. In this work, we study two alternative placement policies considered by the community for dragonfly systems:
